\chapter{Background}

\section*{Introduction}
\paragraph{In order to grasp the full extent of the report, we will delve into the fundamentals and explore the foundational aspects of DevOps.}

\paragraph{DevOps serves as a conceptual framework aimed at reconciling the development and operations aspects of Information Systems. Its primary objective is to dismantle barriers between developers and operations professionals. By implementing a set of principles and practices, DevOps enhances work processes, emphasizing the importance of seamless collaboration between development and operations teams.\cite{diel2016communication}}

\paragraph{Having explored the fundamental concepts and principles of DevOps, we now shift our focus to an integral component of its implementation: Version Control Systems (VCS). In today's fast-paced software development landscape, where collaboration and continuous integration are paramount, VCS plays a crucial role in ensuring seamless coordination, efficient code management, and reliable version tracking. This section delves into the significance of VCS within the DevOps framework, examining its functionalities, benefits, and the popular tools used in the industry. By understanding the pivotal role of version control in enabling successful DevOps practices, we can appreciate its impact on streamlining development processes and fostering a culture of agility and innovation.}

\input{Background/VCS}

Now that we have explored the concept of version control systems in detail, let's shift our gears and dive into the world of Git, one of the most widely used and powerful VCS tools available today.

\input{Background/git}

After grasping the fundamentals of Git, we can now dive into the world of Containers, a powerful technology that enables the creation, deployment, and management of lightweight and portable software environments.

\input{Background/Containers}

\input{Background/Container-Orchestration}

\input{Background/IaC}

\input{Background/CICD}

\input{Background/soft-pracs}